A High Efficiency MAC Protocol for WLANs: Providing Fairness in Dense Scenarios

### 2015-10-16 introProtocol.tex
Closer to the end of the first draft: schedule reset, channel errors and coexistence are done.

	\textcolor{red}{\subsection{Channel errors}}\label{errorEffect}
	Failed transmissions due to channel errors are handled as collisions by CSMA/ECA$_{\text{Hys+FS}}$. This means that a few moments of operation under a noisy channel can increase the contenders's deterministic backoff to its maximum value, carrying the undesired effect of increasing the time between successful transmissions and consequent reduction in the overall system throughput.

@@

	The \emph{Schedule Reset} mechanism for CSMA/ECA$_{\text{Hys+FS}}$ consists on finding the smallest collision-free schedule between a contender's transmissions (if any) and then change the node's deterministic backoff to fit in that schedule. Take a contender with $B_{\text{d}}=32$ as an example. By listening to the slots between its transmissions, it is possible to determine the availability of smaller (and possibly) collision-free schedules.

	Figure~\ref{fig:scheduleReset1} shows the slots between the transmissions of a contender with $B_{\text{d}}=32$. Starting from the left, the current $B_{\text{d}}=0$ means that the next slot will be filled with the contender's own transmission. Each following slot containing either a transmission or a collision is identified with the number one, while empty slots are marked with a zero. Notice that the highlighted empty slots appear every eight slots, suggesting that a schedule reduction from $B_{\text{d}}=32$ to $B_{\text{d}}^{*}=8$ is possible\footnote{$B_{\text{d}}=2^{0}CW_{\min}/2=8$ (see Table~\ref{tab:mac-params}). So the change is made to the backoff stage, $k$. In this case from $2$, to $k=0$. This means that any new schedule must also be a power of two.}. The schedule change is performed after the contender's next successful transmission.

@@

			\begin{algorithm}[tb]
		\If{sxTx == 1}{
			Initialising\;
			\If{B == 0}{
				$b~[B_{\text{d}}] = \{0\}$\;
				$t = 0$\;
			}
		}
		\If{(sxTx $>$ 0) \&\& (sxTx $\leq~\gamma$)}{
			Filling the bitmap\;
			$b[t] \|\sigma_{i}(t)$\label{bitwiseOR}\;
			$t++$\;
			\If{$t == B_{\text{d}} -1$}{
				$t=0$\;
			}
		}
		\If{sxTx == $\gamma$}{\label{evaluations}
			Analising\;
			sxTx = $0$\;
			\For{($j=0;~j<k;~j++$)}{\label{sets}
				$y=2^{j}CW_{\min}/2$\;
				isItPossible $= 0$\;
				\For{($m=y;~m<B_{\text{d}};~m+=y$)}{
					isItPossible$~+=b[m]$\;
				}
				\If{isItPossible == $0$}{
					change = $1$\;
					newStage = $m$\;
					{\bf break};
				}
			}
		}
		\If{change == $1$}{
			Making the change\;
			$k$ = newStage\;
			change = $0$\;
		}
		\vspace{0.2cm}
		\caption{Schedule Reset Mechanism for CSMA/ECA$_{\text{Hys+FS}}$. It is called a \emph{reset} when all smaller deterministic backoff are tested. On the other hand, when $j$ in line~\ref{sets} is initialised to $j=k-1$, it is called a schedule \emph{halving}}\label{alg:schedRest}
	\end{algorithm}

		\subsubsection{Keeping collision-free schedules}
		Schedule Reset is described in Algorithm~\ref{alg:schedRest}. Each contender starts filling a bitmap $b$ of size $B_{\text{d}}$ with the information observed in each passing slot during $\gamma=B_{\text{d}}/C$ consecutive successful transmissions; where $C=2^{m}CW_{\min}/2$ is the biggest deterministic backoff, and $\gamma$ is referred to as the Schedule Reset \emph{threshold} from this point forward.

		Each bit $t,~t\in\{0,\ldots ,B_{\text{d}}-1\}$ in the bitmap is the result of a bitwise OR operation between its current value and the state of the corresponding slot. This is shown in Line~\ref{bitwiseOR} in Algorithm~\ref{alg:schedRest}, where $\sigma_{i}(t)$ is a function that evaluates to $0$ if the slot corresponding to $b[t]$ is empty in iteration $i$, $i \in\{1,\ldots,\gamma\}$; or $1$ otherwise. After $\gamma$ iterations, the bitmap is evaluated. This process starts at Line~\ref{evaluations} in Algorithm~\ref{alg:schedRest}.

@@

		Schedule Reset tests all possible deterministic backoffs that are smaller than the current one. This is done observing the bits in the bitmap corresponding to the tested deterministic backoff. If these slots are empty, the process is stopped and the change to the new deterministic backoff is made.

		Using Figure~\ref{fig:scheduleReset1} as an example, we can see that the sum $\sum\limits_{t} b[t]=0$, for $t\in\{8,16,24\}$. This means that the transmission slots corresponding to a deterministic backoff, $B^{*}_{\text{d}}=8$ are free, therefore a change of schedule is possible.

@@

		\subsubsection{A more aggressive reduction of the schedule}

		The default $\gamma$ ensures that the bitmap registers all the transmission slots in the network (this is true for saturated traffic), providing enough information for performing the schedule reduction without disrupting collision-free schedules. Nevertheless, this $\gamma$ can be rendered too conservative for non-saturated traffic, where contenders enter and leave the contention; or when in the presence of channel errors, where collision-free schedules are disrupted and the schedule of the contenders increases rapidly to its maximum value.

>>>>

	\textcolor{red}{\subsection{Channel errors}}\label{errorEffect}
	Failed transmissions due to channel errors are handled as collisions by CSMA/ECA$_{\text{Hys+FS}}$. Therefore, collision-free schedules under this type of channel model are shorter. In order to accelerate the convergence to collision-free schedules after channel errors CSMA/ECA$_{\text{Hys+FS}}$ instruct nodes to \emph{stick} to the current deterministic backoff even after \emph{stickiness} number of consecutive failed transmissions. Stickiness is not a new concept to CSMA/ECA~\cite{barcelo2011tcf}, it allows for a faster convergence towards a collision-free schedule, especially when performing under heavy channel errors.

	Failed transmissions due to channel errors also means that a few moments of operation under a noisy channel can increase the contenders's deterministic backoff to its maximum value. Such event carries the undesired effects of increasing the time between successful transmissions, and a reduction in the overall system throughput due to shorter collision-free periods.

@@

	The \emph{Schedule Reset} mechanism for CSMA/ECA$_{\text{Hys+FS}}$ consists on finding the smallest collision-free schedule (if any) between a contender's transmissions and then change the node's deterministic backoff to fit in that schedule. Take a contender with $B_{\text{d}}=32$ as an example. By listening to the slots between its transmissions, it is possible to determine the availability of smaller (and possibly) collision-free schedules.

	Figure~\ref{fig:scheduleReset1} shows the slots between the transmissions of a contender with $B_{\text{d}}=32$. Starting from the left, the current $B_{\text{d}}=0$ means that the first slot will be filled with the contender's own transmission. Each following slot containing either a transmission or a collision is identified with the number one, while empty slots are marked with a zero. Notice that the highlighted empty slots appear every eight slots, suggesting that a schedule reduction from $B_{\text{d}}=32$ to $B_{\text{d}}^{*}=8$ is possible\footnote{$B_{\text{d}}=2^{0}CW_{\min}/2=8$ (see Table~\ref{tab:mac-params}). So the change is made to the backoff stage, $k$. In this case from $2$, to $k=0$. This means that any new schedule must also be a power of two.}. The schedule change is performed after the contender's next successful transmission.

@@

			\begin{algorithm}[tb]
		\If{sxTx == 1}{
			Initialising\;
			\If{B == 0}{
				$b~[B_{\text{d}}] = \{0\}$\;
				$t = 0$\;
			}
		}
		\If{(sxTx $>$ 0) \&\& (sxTx $\leq~\gamma$)}{
			Filling the bitmap\;
			$b[t] \|\sigma_{i}(t)$\label{bitwiseOR}\;
			$t++$\;
			\If{$t == B_{\text{d}} -1$}{
				$t=0$\;
			}
		}
		\If{sxTx == $\gamma$}{\label{evaluations}
			Analising\;
			sxTx = $0$\;
			\For{($j=0;~j<k;~j++$)}{\label{sets}
				$y=2^{j}CW_{\min}/2$\;
				isItPossible $= 0$\;
				\For{($m=y;~m<B_{\text{d}};~m+=y$)}{
					isItPossible$~+=b[m]$\;\label{filling}
				}
				\If{isItPossible == $0$}{\label{testFilling}
					change = $1$\;
					newStage = $m$\;
					{\bf break};
				}
			}
		}
		\If{change == $1$}{
			Making the change\;
			$k$ = newStage\;
			change = $0$\;\label{endAssignment}
		}
		\vspace{0.2cm}
		\caption{Schedule Reset Mechanism for CSMA/ECA$_{\text{Hys+FS}}$. Every consecutive successful transmission increases the variable SxTx by one, while a collision resets it to zero. The algorithm is called a \emph{reset} when all smaller deterministic backoff are tested. On the other hand, when $j$ in line~\ref{sets} is initialised to $j=k-1$, it is called a schedule \emph{halving}}\label{alg:schedRest}
	\end{algorithm}

		\subsubsection{Keeping collision-free schedules}
		Schedule Reset is described in Algorithm~\ref{alg:schedRest}. Each contender starts filling a bitmap $b$ of size $B_{\text{d}}$ with the information observed in each passing slot during $\gamma=B_{\text{d}}/C$ consecutive successful transmissions (sxTx in Algorithm~\ref{alg:schedRest}); where $C=2^{m}CW_{\min}/2$ is the biggest deterministic backoff, and $\gamma$ is referred to as the Schedule Reset \emph{threshold} from this point forward.

		Each bit $t,~t\in\{0,\ldots ,B_{\text{d}}-1\}$ in the bitmap is the result of a bitwise OR operation between its current value and the state of the corresponding slot. This is shown in Line~\ref{bitwiseOR} in Algorithm~\ref{alg:schedRest}, where $\sigma_{i}(t)$ is a function that evaluates to $0$ if the slot corresponding to $b[t]$ is empty in iteration $i$, $i \in\{1,\ldots,\gamma\}$; or $1$ otherwise. After $\gamma$ iterations, the bitmap is evaluated (line~\ref{evaluations} in Algorithm~\ref{alg:schedRest}).

@@

		Schedule Reset tests all possible deterministic backoffs that are smaller than the current $B_{\text{d}}$ (lines~\ref{sets}-\ref{filling} in Algorithm~\ref{alg:schedRest}), starting with the smallest one. If the corresponding bits in the bitmap are registered as empty, the process is stopped and the change to the new deterministic backoff is made (lines~\ref{testFilling}-\ref{endAssignment} in Algorithm~\ref{alg:schedRest}). Otherwise, the process is restarted after the next successful transmission.

		Using Figure~\ref{fig:scheduleReset1} as an example, we can see that the sum $\sum\limits_{t} b[t]=0$, for $t\in\{8,16,24\}$. This means that the transmission slots corresponding to a deterministic backoff, $B^{*}_{\text{d}}=8$ are free, therefore a change of schedule is possible. In case of suffering a collision immediately after applying the schedule reduction, the node reverses the changes made by Schedule Reset before handling the collision.

@@

		\subsubsection{Facing channel errors}\label{aggr}

		the default $\gamma$ ensures that the bitmap registers all the transmission slots in the network (assuming saturated traffic and a perfect channel), providing enough information for performing the schedule reduction without disrupting collision-free schedules.

		Nevertheless, this $\gamma$ can be rendered too conservative when in the presence of channel errors. This condition produces Schedule Reset bitmaps that do not contain enough information for successfully avoiding collisions after the schedule reduction. This is also true for any $\gamma^{*}>\gamma$.

### 2015-10-16 results.tex
Closer to the end of the first draft: schedule reset, channel errors and coexistence are done.

	This section aims at overviewing the throughput of CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ in saturation, as well as the collision probability, the average time between successful transmissions and the effect of clock drift over the throughput.
	\\
	\subsubsection{Throughput}
	CSMA/ECA$_{\text{Hys+FS}}$ nodes are able to build a collision-free schedule, use the channel more efficiently and experience a throughput increase, as seen in Figure~\ref{fig:throughput-sat}. As mentioned in Section~\ref{moreContenders}, Hysteresis allows the allocation of more contenders in a collision-free schedule, while Fair Share ensures an even distribution of the available throughput. In contrast, CSMA/CA throughput keeps decreasing due to an augmented number of collisions as the number of nodes increases (see Figure~\ref{fig:collisions-sat}). Further, Figure~\ref{fig:collisions-evolution} shows the fraction of collision slots for CSMA/ECA$_{\text{Hys+FS}}$ and CSMA/CA as simulation time passes. In the figure, is appreciated how the fraction of collision slots keeps decreasing once CSMA/ECA$_{\text{Hys+FS}}$ reaches the collision-free schedule.

@@

	After 40 contenders, the MAC queue of CSMA/ECA$_{\text{Hys+FS}}$ nodes starts to fill, as appreciated in Figure~\ref{fig:MacQ}, gradually building a collision-free schedule due to CSMA/ECA$_{\text{Hys+FS}}$'s deterministic backoff after successful transmissions. This allows CSMA/ECA$_{\text{Hys+FS}}$ to outperform CSMA/CA.\\

@@

   	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/droppedPackets/droppedPacketsDueRET-TON.eps}
		\caption{Percentage of droppped packets due to reaching the retransmission threshold}
		\label{fig:droppedDueToRET}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/timeBetweenSxTx-unsat/timeBetweenSxTx-multiplot-unsat-TON.eps}
		\caption{Average time between successful transmissions in non-saturated conditions: averaging over all stations}
		\label{fig:timeBetweenSxTx-multiplot-unsat}
	\end{figure}

@@

	\begin{figure}[tb!!!]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/mixed/throughput-mixed/throughput-unsaturated-mixed-TON.eps}
		\caption{Network throughput when composed by various proportions of non-saturated CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes}
		\label{fig:mixedThroughput-unsat}
	\end{figure}

	\begin{figure}[tb!!!]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/mixed/collisions-mixed/collisions-mixed-unsaturated-TON.eps}
		\caption{Average percentage of collision slots for the tested mixed network setups proportions in non-saturated conditions}
		\label{fig:mixCollisions-unsat}
	\end{figure}

	In the figure it is appreciated how the mixed network setups curves lay between the CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ curves. As the proportion of CSMA/CA nodes decreases, the throughput increases as the result of a lower probability of collision, as can be seen in Figure~\ref{fig:mixedCollisions-sat}. A similar behavior is observed when testing the same proportion of nodes under non-saturated conditions. Figure~\ref{fig:mixedThroughput-unsat} and Figure~\ref{fig:mixCollisions-unsat} show the average aggregated throughput and fraction of collisions slots in a non-saturated mixed network setup.

@@

>>>>

	This section aims at overviewing the throughput of CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ in saturation, as well as the collision probability, the average time between successful transmissions and the effect of clock drift over the throughput.
	\\
	\subsubsection{Throughput}
	CSMA/ECA$_{\text{Hys+FS}}$ nodes are able to build a collision-free schedule, use the channel more efficiently, and experience a throughput increase as seen in Figure~\ref{fig:throughput-sat}. Hysteresis allows the allocation of more contenders by increasing the length of the collision-free schedule, while Fair Share ensures an even distribution of the available throughput. This is reflected by the average backoff stage, which value increases with the number of contenders. In contrast, CSMA/CA throughput keeps decreasing due to an augmented number of collisions as the number of nodes increases (see Figure~\ref{fig:collisions-sat}). Further, Figure~\ref{fig:collisions-evolution} shows the fraction of collision slots for CSMA/ECA$_{\text{Hys+FS}}$ and CSMA/CA as simulation time passes. In the figure, is appreciated how the fraction of collision slots keeps decreasing once CSMA/ECA$_{\text{Hys+FS}}$ reaches the collision-free schedule.

@@

	\textcolor{red}{As indicated by Figure~\ref{fig:collisions-unsat}, when $20<N\leq 35$ CSMA/ECA$_{\text{Hys+FS}}$ nodes suffer from an increasing number of  collisions. This is due to nodes entering the contention with a random backoff every time a new packet arrives at their empty MAC queues. Beyond 35 contenders, the MAC queue of CSMA/ECA$_{\text{Hys+FS}}$ nodes starts to fill up, as appreciated in Figure~\ref{fig:MacQ}, gradually allowing the construction of longer collision-free schedules due to CSMA/ECA$_{\text{Hys+FS}}$ nodes getting saturated}. This allows CSMA/ECA$_{\text{Hys+FS}}$ to outperform CSMA/CA.\\

@@

   	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/droppedPackets/droppedPacketsDueRET-TON.eps}
		\caption{Percentage of droppped packets due to reaching the retransmission threshold. CSMA/ECA$_{\text{Hys+FS}}$ has an increased metric because the number of dropped packets is determined by Fair Share, i.e.: drops $2^{k}$ packets, where $k$ is the current backoff stage of the node}
		\label{fig:droppedDueToRET}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/timeBetweenSxTx-unsat/timeBetweenSxTx-multiplot-unsat-TON.eps}
		\caption{Average time between successful transmissions in non-saturated conditions: averaging over all stations. \textcolor{red}{this figure needs new data files}}
		\label{fig:timeBetweenSxTx-multiplot-unsat}
	\end{figure}

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/mixed/throughput-mixed/throughput-unsaturated-mixed-TON.eps}
		\caption{Network throughput when composed by various proportions of non-saturated CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes}
		\label{fig:mixedThroughput-unsat}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/mixed/collisions-mixed/collisions-mixed-unsaturated-TON.eps}
		\caption{Average percentage of collision slots for the tested mixed network setups proportions in non-saturated conditions}
		\label{fig:mixCollisions-unsat}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/saturated/mixed/throughput-per-protocol/throughput-per-protocol-TON.eps}
		\caption{Average throughput per MAC protocol in a saturated mixed network}
		\label{fig:mixThroughput-sat-perProtocol-TON}
	\end{figure}

	In the figure it is appreciated how the mixed network setups curves lay between the CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ curves. As the proportion of CSMA/CA nodes decreases, the throughput increases as the result of a lower probability of collision, as can be seen in Figure~\ref{fig:mixedCollisions-sat}. A similar behaviour is observed when testing the same proportion of nodes under non-saturated conditions. Figure~\ref{fig:mixedThroughput-unsat} and Figure~\ref{fig:mixCollisions-unsat} show the average aggregated throughput and fraction of collisions slots in a non-saturated mixed network setup.

@@

	\textcolor{red}{Figure~\ref{fig:mixThroughput-sat-perProtocol-TON} shows the average throughput for CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ stations in a saturated mixed setup (half the contenders using CSMA/CA). It is possible to see that for a low total contenders ($N^{*}\leq 12$) CSMA/CA stations attain greater throughput than in a CSMA/CA-only network. This is because in the mixed network setup the other $N^{*}/2$ contenders with CSMA/ECA$_{\text{Hys+FS}}$ use a deterministic backoff, leaving many empty slots between transmissions. This reduces the chances of collisions for CSMA/CA nodes when compared with a CSMA/CA-only network and the same number of total contenders.}

	\textcolor{red}{Still referring to Figure~\ref{fig:mixThroughput-sat-perProtocol-TON}, for $N^{*}>12$ periods of collision-free operation and the aggregation performed with Fair Share allows CSMA/ECA$_{\text{Hys+FS}}$ to have larger channel time than CSMA/CA nodes, which throughput degrades even more than in CSMA/CA-only networks.}

	\textcolor{red}{\subsection{Saturation, channel errors and Schedule Reset}\label{resultsSchedRest}}
	\textcolor{red}{Figure~\ref{fig:throughput-sat-SR} shows the average aggregated throughput of a non-saturated network with a channel error probability, $p_e=0.1$ (see Section~\ref{channelErrorsDef}). We can see that the highest throughput, corresponding to CSMA/ECA$_{\text{Hys+FS}}$ is lower than the one observed in a perfect channel (Figure~\ref{fig:throughput-sat}). Furthermore, curves with Schedule Reset (SR) seem to have lower aggregated throughput. This is because the backoff stage, and therefore the level of aggregation done by Fair Share, is constantly reduced.}

	\textcolor{red}{Still assessing Figure~\ref{fig:throughput-sat-SR} and focusing on the SR curves, we can see that both \emph{SR aggr. halv. dynStick} curves (with and without Fair Share) have higher aggregated throughput than the rest. This Schedule Reset configuration shows higher aggregated throughput because it reduces the time between successful transmissions (see Figure~\ref{fig:timeBetSxTx-sat-SR}) and mantains collision-free schedules for longer periods of time thanks to the increase in the node's stickiness.}

	\textcolor{red}{Figure~\ref{fig:timeBetSxTx-sat-SR} shows the average time between successful transmissions for the same network setup. Even-though CSMA/ECA$_{\text{Hys+FS}}$ still has a higher metric than CSMA/CA due to the aggregation done by Fair Share, Schedule Reset is able of reducing this metric by almost a $43\%$.}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/tonFigs/throughput-sat-SR-TON.eps}
		\caption{Average throughput for a saturated network with channel error ($p_e=0.1$). Curves called "aggr" reffer to values of $\gamma=1$, while "halv" refers to a schedule halving (see Section~\ref{aggr} and Algorithm~\ref{alg:schedRest}). \emph{dynStick} reffers to curvers where the node's stickiness is temporarily increased to two after a successful reduction of the schedule. \textcolor{red}{this figure needs new data files}}
		\label{fig:throughput-sat-SR}
	\end{figure}

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/tonFigs/timeBetSxTx-sat-SR-TON.eps}
		\caption{Time between successful transmissions for a saturated network with channel error ($p_e=0.1$). Curves called "aggr" reffer to values of $\gamma=1$, while "halv" refers to a schedule halving (see Section~\ref{aggr} and Algorithm~\ref{alg:schedRest}). \emph{dynStick} reffers to curvers where the node's stickiness is temporarily increased to two after a successful reduction of the schedule. \textcolor{red}{this figure needs new data files}}
		\label{fig:timeBetSxTx-sat-SR}
	\end{figure}

### 2015-10-16 simulations.tex
Closer to the end of the first draft: schedule reset, channel errors and coexistence are done.

	The aforementioned assumptions ensure that the simulation results are just effects of the MAC behaviour.
	%Further, in a collision-free CSMA/ECA$_{\text{Hys+FS}}$ operation there is no need for RTS/CTS mechanisms, given that successful nodes already know their respective transmission slot. \textcolor{red}{Maybe here is where the conversation about hidden nodes should take place?}
	If not mentioned otherwise, results are derived from 100 simulations of 100 seconds in length. Figures also show the standard deviation.

@@

	\textcolor{red}{\subsection{Channel errors} 
	We model channel errors by assigning a probability of a packet being corrupted by the channel, $p_e>0$. That is, in a single packet transmission there is probability $p_e$ that the transmission will not be acknowledged. If the transmission is an A-MPDU (like in the case of CSMA/ECA$_{\text{Hys+FS}}$), $p_e$ will affect each packet individually and independently. Therefore, a A-MPDU transmission will be considered a failure is all packets in the aggregation are affected by the channel error probability.}

@@

@@

>>>>

	The aforementioned assumptions ensure that the simulation results are just effects of the MAC behaviour.
	%Further, in a collision-free CSMA/ECA$_{\text{Hys+FS}}$ operation there is no need for RTS/CTS mechanisms, given that successful nodes already know their respective transmission slot. \textcolor{red}{Maybe here is where the conversation about hidden nodes should take place?}
	If not mentioned otherwise, results are derived from \textcolor{red}{20 simulations of 100 seconds in length, each one with a different seed}. Figures also show the standard deviation.

@@

@@

	\textcolor{red}{\subsection{Channel errors}\label{channelErrorsDef}
	Channel errors are modelled by assigning a probability of a packet being corrupted by the channel, $p_e>0$. That is, in a single packet transmission there is probability $p_e$ that the transmission will not be acknowledged. If the transmission is an A-MPDU (like in the case of CSMA/ECA$_{\text{Hys+FS}}$), $p_e$ will affect each packet individually and independently. Therefore, an A-MPDU transmission will be considered a failure if all packets in the aggregation are affected by the channel error probability.}

	\textcolor{red}{All results are shown with stickiness equal to one (see Section~\ref{errorEffect}). That is, after a colision, CSMA/ECA$_{\text{Hys+FS}}$ nodes will use a random backofff. Nevertheless, in Section~\ref{resultsSchedRest} curves described as \emph{dynStick} temporarily increase the node's stickiness to two after a successful reduction of the schedule (using a random backoff after two consecutive collisions). This increase is done in order to converge faster to collision-free schedules when in operating with channel errors.}

@@

	\textcolor{red}{\subsection{Applying Schedule Reset} 
	A set of results under saturated conditions and channel errors applying Schedule Reset (see Section~\ref{schedReset}) are provided. Some of the results are generated with a $\gamma=1$, or \emph{aggressive} Schedule Reset (aggr. in the figures). These settings provide the highest throughput under the tested conditions, and also in the real hardware implementations such as the one shown in Section~\ref{EDCA}.
	}
